Cannibalism among the supermassive black holes

### 2016-09-15 paper.tex
added figure for BH masses
Added tables of merger results

\documentclass[english, apj]{emulateapj}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{array}
\usepackage{rotating}
\usepackage{units}
\usepackage{textcomp}
\usepackage{amsmath}
\usepackage{amsbsy}
\usepackage{amstext}
\usepackage{graphicx}
\usepackage{url}
\usepackage{babel}
\usepackage[backref,breaklinks,colorlinks,citecolor=blue]{hyperref}
\usepackage[all]{hypcap}
%\usepackage{siunitx}

@@

Starting with this data, we plotted the galaxy masses as a function of time.  Since the raw data was given in terms of redshift, we converted redshift to time with the help of a 'cosmology calculator', courtesy of Ned Wright and James Schombert (\url{http://www.astro.ucla.edu/~wright/CosmoCalc.html}).  We chose three galaxies to run our simulations.  The galaxies were chosen using the following basic criteria:
\begin{itemize}
\item The galaxies had to exist through the entire simulation, from $z=4$ to $z=0$.
\item They had to have a central SMBH.
\item They had to have at least XXX orbiting black holes.
\item We ordered the galaxies by decreasing mass at $z=0$, and starting with the largest tier of mass (~$10^{14} M_{\odot}$), we spaced their masses by approximately 1-2 orders of magnitude.
\end{itemize}

@@

@@

\subsection{Mergers}
\noindent A: two mergers early on, and then two more at around 10-12 Gyr\\
B: 4 mergers across the final 8 Gyr\\
C: two mergers in the final Gyrs\\
D: ?\\

>>>>

\documentclass[english, apj]{emulateapj}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{array}
\usepackage{rotating}
\usepackage{units}
\usepackage{textcomp}
\usepackage{amsmath}
\usepackage{amsbsy}
\usepackage{amstext}
\usepackage{graphicx}
\usepackage{url}
\usepackage{babel}
%\usepackage{siunitx}
%\sisetup{output-exponent-marker=\ensuremath{\mathrm{e}}}
\usepackage[backref,breaklinks,colorlinks,citecolor=blue]{hyperref}
\usepackage[all]{hypcap}

@@

Starting with this data, we plotted the galaxy masses as a function of time.  Since the raw data was given in terms of redshift, we converted redshift to time with the help of a 'cosmology calculator', courtesy of Ned Wright and James Schombert (\url{http://www.astro.ucla.edu/~wright/CosmoCalc.html}).  We chose four galaxies to run our simulations.  The galaxies were chosen using the following basic criteria:
\begin{itemize}
\item The galaxies had to exist through the entire simulation, from $z=4$ to $z=0$.
\item They had to have a central SMBH.
\item They had to have at least XXX orbiting black holes.
\item We ordered the galaxies by decreasing mass at $z=0$, and starting with the largest tier of mass (~$10^{14} M_{\odot}$), we spaced their masses by approximately 1-2 orders of magnitude.
\end{itemize}

@@

\subsection{Description of Simulations}
\begin{table}
\caption{Merger Results}
\begin{tabular}{c c c c}
\hline\hline \\
Galaxy & Orbiting BHs & $t_{fric}<100*t_H$ & Simulation Mergers \\
A & 206 & 19 & 4 \\
B & 29 & 12 & 4 \\
C & 3 & 3 & 2 \\
D & 4 & 4 & 2 \\
\end{tabular}
\end{table}

\begin{table}
\caption{Galaxies used in Simulation}
\begin{tabular}{c| c c| c c| c c|}
\hline\hline \\
& \multicolumn{2}{c}{$M_{gal}$ [$M_{\odot}$]} & 
\multicolumn{2}{c}{$M_{*}$ [$M_{\odot}$]} & 
\multicolumn{2}{c}{$M_{BH}$ [$M_{\odot}$]} \\
Galaxy & Init & Final & Init & Final & Init & Final \\
A & $7.42\mathrm{e}{11}$ & $1.09\mathrm{e}{14}$  & $1.22\mathrm{e}{11}$ & $1.75\mathrm{e}{13}$ & $4.80\mathrm{e}{06}$ & $2.19\mathrm{e}{09}$\\
B & $1.11\mathrm{e}{12}$ & $3.41\mathrm{e}{13}$ & $1.80\mathrm{3}{11}$ & $5.58\mathrm{e}{12}$ & $1.94\mathrm{e}{08}$ & $1.46\mathrm{e}{09}$\\
C & $7.23\mathrm{e}{10}$ & $3.48\mathrm{e}{12}$ & $1.18\mathrm{e}{10}$ & $5.68\mathrm{e}{11}$ & $9.47\mathrm{e}{04}$ & $2.70\mathrm{e}{08}$\\
D & $3.92\mathrm{e}{10}$ & $1.34\mathrm{e}{12}$ & $6.47\mathrm{e}{9}$ & $2.20\mathrm{e}{11}$ & $9.95\mathrm{e}{05}$ & $8.32\mathrm{e}{07}$\\
\end{tabular}
\end{table}

@@

\subsection{Mergers}
\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.45\textwidth]{plots/masses_ABCD.png}
\caption{default}
\label{default}
\end{center}
\end{figure}

\noindent A: two mergers early on, and then two more at around 10-12 Gyr\\
B: 4 mergers across the final 8 Gyr\\
C: two mergers in the final Gyrs\\
D: ?\\
